### 2021-04-22 latex/article/article.tex
update

 \begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/emm_emp_contour.pdf}
    \end{center}
    \caption{}\label{fig:emm_emp_contour}
 \end{figure}
At $90\%$ CL:
PINGU: $-0.046 < \emm < 0.041$
DC: $-0.045 < \emm < 0.041$
joint: $-0.038 < \emm < 0.033$
\begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/track_flux_ratio.pdf}
       \includegraphics[width=0.4\linewidth]{figures/cascade_flux_ratio.pdf}
    \end{center}
    \caption{Ratio of NSI to SI atmospheric fluxes at detector level. Dotted (dashed) lines show the region in which 99\% of the 
    DeepCore (IceCube) MC events are contained.}\label{fig:flux_ratio}
 \end{figure}
\bibliographystyle{elsarticle-num}
\bibliography{article}
\end{document}

>>>>

 \begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/emm_emp_contour.pdf}
    \end{center}
    \caption{}\label{fig:emm_emp_contour}
 \end{figure}
At $90\%$ CL:
PINGU: $-0.046 < \emm < 0.041$
DC: $-0.045 < \emm < 0.041$
joint: $-0.038 < \emm < 0.033$
\begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/track_flux_ratio.pdf}
       \includegraphics[width=0.4\linewidth]{figures/cascade_flux_ratio.pdf}
    \end{center}
    \caption{Ratio of NSI to SI atmospheric fluxes at detector level. Dotted (dashed) lines show the region in which 99\% of the 
    DeepCore (IceCube) MC events are contained.}\label{fig:flux_ratio}
 \end{figure}

 \newpage
\begin{tabular}{p{55mm}p{55mm}p{55mm}}
   DeepCore (2017)
      \begin{itemize}
         \item[$\checkmark$] Honda atmospheric fluxes
         \item[$\times$] Only look at tracks and $\emt$
         \vspace{1em}  
         \item[$\times$] DC Monte Carlo from an older dataset 
         \item[$\times$] 8 E bins from $\SI{6.3}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
         \item[$\times$] 8 z bins from -1 to 0 
         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
         \item[$\times$] Prior on spectral index
         \item[$\times$] No zenith angle normalization
         \item[$\checkmark$] No priors on $\Delta m_{31}^2, \theta_{23},\theta_{13}$
      \end{itemize} &
    Demidov (2020) DC analysis
      \begin{itemize}
         \item[$\checkmark$] Honda atmospheric fluxes
         \item[$\checkmark$] Looks at tracks + cascades for $\emt$ and $\ett$
         \item[$\checkmark$] Data and Monte Carlo from DC 2018
         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
         \item[$\checkmark$] 8 z bins from -1 to 1
         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
         \item[$\times$] Prior on spectral index
         \item[$\times$] No zenith angle normalization
         \item[$\checkmark$] No priors on $\Delta m_{31}^2, \theta_{23}$
         \item[$\checkmark$] Fixes $\Delta m^2_{21}, \theta_{12}, \theta_{13}$
         \item[$\times$] Uncertainty on hadron production in atmosphere
         \item[$\times$] Uncertainty on neutrino nucleon cross section 
      \end{itemize} &
    Choubey et. al. PINGU analysis
      \begin{itemize}
         \item[$\checkmark$] Honda atmospheric fluxes
         \item[$\times$] Only consider $\nm$ events
         \vspace{1em} 
         \item[$\times$] $A_\text{eff}$ and resolution from PINGU Letter of intent
         \item[$\times$] 27 E bins from 2 to $\SI{101}{\electronvolt^2}$
         \item[$\times$] 10 z bins from -1 to 0
         \item[$\checkmark$] Flux normalization uncertainty of 20\%
         \item[$\times$] Uncertanties in cross-section and spectral index 
         \item[$\checkmark$] Zenith angle uncertainty of 5\% 
         \item[$\times$] Priors on $\Delta m_{31}^2, \theta_{23},\theta_{13}$
      \end{itemize} 
\end{tabular}

\bibliographystyle{elsarticle-num}
\bibliography{article}
\end{document}
